Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-05-27 writeup/gz_hubble_data.tex
Re-ordering authors and adding affiliations.

%% Authors with the same affiliation can be grouped in a single
%% \author and \affil call.
\author{Kyle W. Willett\altaffilmark{1,2}, Melanie A. Galloway\altaffilmark{1}, Karen L. Masters\altaffilmark{3,4}, B.D. Simmons\altaffilmark{5,6,7}, Chris J. Lintott\altaffilmark{5}, Steven P. Bamford\altaffilmark{8}, Edmond Cheung\altaffilmark{9}, Tom Melvin\altaffilmark{3}, Lucy F. Fortson\altaffilmark{1}, Melanie Beck\altaffilmark{1}, Claudia Scarlata\altaffilmark{1}, Roger L. Griffith\altaffilmark{10,11}, Kevin Schawinski\altaffilmark{12}, Edward M. Edmondson\altaffilmark{3}, Arfon M. Smith\altaffilmark{5,13,14}, Michael Parrish\altaffilmark{13}, Anna Han\altaffilmark{15}
}
%
%$^N$Institute for Cosmology and Gravitation, University of Portsmouth, Dennis Sciama Building, Burnaby Road, Portsmouth, PO1 3FX, UK \\
%$^N$South East Physics Network, www.sepnet.ac.uk\\
%$^N$Dept. of Astronomy, Cornell University, Space Sciences Building, Ithaca, NY 14850, USA\\
%$^N$Institute for Sciences of the Cosmos (ICCUB), University of Barcelona, Marti i Franques 1, Barcelona, 08024 Spain\\
%$^N$Oxford Astrophysics, Department of Physics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK\\
%$^N$Yale Center for Astronomy and Astrophysics, Yale University, P.O. Box 208121, New Haven, CT 06520, USA \\
%$^N$Steward Observatory, University of Arizona, 933 N. Cherry Ave, Tuscon, AZ 85721, USA\\
%$^N$Astronomy Department, Adler Planetarium and Astronomy Museum, 1300 Lake Shore Drive, Chicago, IL 60605, USA\\
%$^N$Centre for Astronomy \& Particle Theory, University of Nottingham, University Park, Nottingham, NG7 2RD, UK\\
%$^N$School of Physics and Astronomy, University of Minnesota, Minneapolis, MN 55455, USA\\
%$^N$Department of Physics \& Astronomy, 206 Gallalee Hall, 514 University Blvd., University of Alabama, Tuscaloosa, AL 35487-0234, USA\\
%$^N$Einstein Fellow\\

%\altaffiltext{1}{School of Physics and Astronomy, University of Minnesota, USA}
%\altaffiltext{2}{Department of Physics and Astronomy, University of Kentucky, USA}
%\altaffiltext{3}{Oxford Astrophysics, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK}
%\altaffiltext{4}{Center for Astrophysics and Space Sciences (CASS), Department of Physics, University of California, San Diego, CA 92093, USA}
%\altaffiltext{5}{Balliol College}
%\altaffiltext{6}{Einstein Fellow}
%\altaffiltext{7}{Institute of Cosmology and Gravitation, University of Portsmouth, UK}
%\altaffiltext{8}{SEPnet, South East Physics Network, UK}
%\altaffiltext{9}{University of Nottingham, UK}
%\altaffiltext{10}{ETH Z\"urich, Switzerland}
%\altaffiltext{11}{Kavli Institute for the Physics and Mathematics of the Universe (WPI), Japan}
%\altaffiltext{12}{Adler Planetarium, USA}
%\altaffiltext{13}{GitHub}
%\altaffiltext{14}{University of California, Berkeley, USA}
%\altaffiltext{15}{Penn State University, USA}
%\altaffiltext{16}{Yale University, USA}

>>>>

%% Authors with the same affiliation can be grouped in a single
%% \author and \affil call.
\author{
    Kyle W. Willett\altaffilmark{1,2}, 
    Melanie A. Galloway\altaffilmark{1}, 
    Steven P. Bamford\altaffilmark{3}, 
    Chris J. Lintott\altaffilmark{4}, 
    Karen L. Masters\altaffilmark{5,6}, 
    Claudia Scarlata\altaffilmark{1}, 
    B.D. Simmons\altaffilmark{4,7}, 
    Melanie Beck\altaffilmark{1}, 
    Carolin N. Cardamone\altaffilmark{8}, 
    Edmond Cheung\altaffilmark{9}, 
    Edward M. Edmondson\altaffilmark{5}, 
    Lucy F. Fortson\altaffilmark{1},
    Roger L. Griffith\altaffilmark{10,11}, 
    Boris H\"au{\ss}ler\altaffilmark{4,12,13},
    Anna Han\altaffilmark{14}, 
    Ross Hart\altaffilmark{3}, 
    Tom Melvin\altaffilmark{5}, 
    Michael Parrish\altaffilmark{15}, 
    Kevin Schawinski\altaffilmark{16}, 
    R.J. Smethurst\altaffilmark{4}, 
    Arfon M. Smith\altaffilmark{5,15,17}
}
%
%$^N$Institute for Cosmology and Gravitation, University of Portsmouth, Dennis Sciama Building, Burnaby Road, Portsmouth, PO1 3FX, UK \\
%$^N$South East Physics Network, www.sepnet.ac.uk\\
%$^N$Dept. of Astronomy, Cornell University, Space Sciences Building, Ithaca, NY 14850, USA\\
%$^N$Institute for Sciences of the Cosmos (ICCUB), University of Barcelona, Marti i Franques 1, Barcelona, 08024 Spain\\
%$^N$Oxford Astrophysics, Department of Physics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK\\
%$^N$Yale Center for Astronomy and Astrophysics, Yale University, P.O. Box 208121, New Haven, CT 06520, USA \\
%$^N$Steward Observatory, University of Arizona, 933 N. Cherry Ave, Tucson, AZ 85721, USA\\
%$^N$Astronomy Department, Adler Planetarium and Astronomy Museum, 1300 Lake Shore Drive, Chicago, IL 60605, USA\\
%$^N$Centre for Astronomy \& Particle Theory, University of Nottingham, University Park, Nottingham, NG7 2RD, UK\\
%$^N$School of Physics and Astronomy, University of Minnesota, Minneapolis, MN 55455, USA\\
%$^N$Department of Physics \& Astronomy, 206 Gallalee Hall, 514 University Blvd., University of Alabama, Tuscaloosa, AL 35487-0234, USA\\
%$^N$Einstein Fellow\\

\altaffiltext{1}{School of Physics and Astronomy, University of Minnesota, USA}
\altaffiltext{2}{Department of Physics and Astronomy, University of Kentucky, USA}
\altaffiltext{3}{School of Physics and Astronomy, University of Nottingham, UK}
\altaffiltext{4}{Oxford Astrophysics, University of Oxford, UK}
\altaffiltext{5}{Institute of Cosmology and Gravitation, University of Portsmouth, UK}
\altaffiltext{6}{SEPnet, South East Physics Network, UK}
\altaffiltext{7}{Center for Astrophysics and Space Sciences, UC San Diego, USA}
\altaffiltext{8}{Department of Mathematics and Science, Wheelock College, USA}
\altaffiltext{9}{Kavli Institute for the Physics and Mathematics of the Universe (WPI), Japan}
\altaffiltext{10}{Infrared Processing and Analysis Center, California Institute of Technology, USA}
\altaffiltext{11}{Department of Astronomy and Astrophysics, Pennsylvania State University, USA}
\altaffiltext{12}{Centre for Astrophysics, University of Hertfordshire, UK}
\altaffiltext{13}{European Southern Observatory, Santiago, Chile}
\altaffiltext{14}{Department of Astronomy, Yale University, USA}
\altaffiltext{15}{Adler Planetarium, USA}
\altaffiltext{16}{Institute for Astronomy, ETH Z\"urich, Switzerland}
\altaffiltext{17}{GitHub}
